Semantic browsing of sound databases \\ without keywords

### 2016-02-11 lafaySsf2016.tex
newversion

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{gfx/SSF.pdf} 
\end{center}
\caption{\label{figSSF} Spatial configuration of the Progressive Display (PD) based on the semantic hierarchical structure of the dataset}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.18]{gfx/XP3.pdf} 
\end{center}
\caption{\label{figXP3} Acoustical Display (AD) \gregoire{fill the dots ;)}}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse1} 
\end{center}
\caption{\label{fig1} Average and standard deviation for (a) the total search durations, (b) the total search durations and (c) the total search durations}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse2} 
\end{center}
\caption{\label{fig2} Medians of (top) the numbers of heard sounds at each target sound search, (middle) the numbers of heard sounds without duplication (WD) at each target sound search, (bottom) the relative durations at each target sound search \gregoire{polynomial beautiful regression} }
\end{figure}

@@

Figure~\ref{fig1}~(c) shows the results for the number of unique heard sounds. This time the results of AD are significantly lower than those of both PD and FD (AD-PD: $p<0.01$; AD-FD: $p<0.01$).  For AD, 75\% of the subjects heard more than 138 sounds, and 25\% heard 148 sounds, that is almost the entire database. Considering PD, 75\% of subjects heard  less than 133 sounds, against 144 for FD. This time PD and FP seem to perform equally (PD-FD: $p=0.58$)

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.24]{gfx/SSF.pdf} 
\end{center}
\caption{\label{figSSF} Spatial configuration of the Progressive Semantic Display (PSD) based on the semantic hierarchical structure of the dataset}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.18]{gfx/XP3.pdf} 
\end{center}
\caption{\label{figXP3} Acoustical Display (AD)}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse1.eps} 
\end{center}
\caption{\label{fig1} Average and standard deviation for (a) the total search durations, (b) the number of heard sounds and (c) the number of unique heard sounds}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{gfx/analyse2.eps} 
\end{center}
\caption{\label{fig2} evolution of (a) the average search durations, (b) the average numbers of heard sounds, and (c) average the numbers of unique heard sounds at each target sound search. Lines are linear regression.}
\end{figure}

@@

Figure~\ref{fig1}~(c) shows the results for the number of unique heard sounds. This time the results of AD are significantly lower than those of both PD and FD (AD-PD: $p<0.01$; AD-FD: $p<0.01$).  For AD, 75\% of the subjects heard more than 140 sounds, and 25\% heard at least 148 sounds, that is almost the entire database. Considering PSD, 75\% of subjects heard  less than 134 sounds, against 143 for FSD. This time PSD and FSD seem to perform equally (PD-FD: $p=0.58$)
